\documentclass[letterpaper, 10 pt,conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
\usepackage{graphicx} % for pdf, bitmapped graphics files
\graphicspath{{../}}
\usepackage{epstopdf} % for postscript graphics files
\usepackage{mathptmx} % assumes new font selection scheme installed
\usepackage{times} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{fixltx2e}
\usepackage{float}

\title{\LARGE \bf
3D-PIV application for autonomous vehicles using monocular vision
}


\author{Eduardo da Silva Afonso$^{1}$ and Fernando Pujaico Rivera$^{2}$ and Arthur de Miranda Neto$^{3}$% <-this % stops a space
\thanks{The authors are with Terrestrial Mobility Lab. at the Federal University of Lavras, Lavras - MG, Brazil.}%
\thanks{$^{1}$  eduardo.afonso@engautomacao.ufla.br, $^{2}$  201518201@posgrad.ufla.br, $^{3}$  arthur.miranda@deg.ufla.br}%
}

\begin{document}


\maketitle
\thispagestyle{empty}
\pagestyle{empty}

\begin{abstract}

\input{sections/abst}

\end{abstract}
\input{sections/introduction}


\section{THEORETICAL FUNDAMENT}
\input{sections/pearson}
\input{sections/particle}


\section{SYSTEM DESCRIPTION}
\input{sections/systemdesc}

\section{ALGORITHM DESCRIPTION}
 
%DiagramaX
\input{sections/multires}
\input{sections/multires3d}
\input{sections/newroi}

% descrição do sistemA
\section{NUMERICAL RESULTS}
\input{sections/results}
%testes com diferentes parametros
% tabelas e graficos

\section{CONCLUSIONS}
\input{sections/conclu}
\addtolength{\textheight}{-12cm}

\section*{ACKNOWLEDGMENT}

\input{sections/ackn}

%FAPEMIG\\
%numero de bolsa\\
%numero de projeto\\
%numero de aluno


\begin{thebibliography}{99}
	\bibitem{Bastiaans} R. J. M. Bastiaans, Cross-correlation PIV; theory, implementation and accuracy. 
        Eindhoven: Technische Universiteit Eindhoven, 2000. - EUT Report 99-W-OOl. - ISBN: 90-386-2851-X.

	\bibitem{Story} A. Story et al, PIV measurements of the velocity field of a Newtonian Fluid in a stirred tank equipped 
	with the PMT type impeller.Technical Transactions - Chemistry. 2-Ch/2014.        

	\bibitem{Xu} L. Xu, Computational fluid dynamics analysis and PIV validation of a bionic vortex flow 
	pulsatile LVAD.Technology and Health Care 23 (2015) S443?S451. DOI 10.3233/THC-150981. IOS Press, 2015.
	
        \bibitem{Miranda Neto} A. Miranda Neto et al, Image Processing Using Pearson's Correlation Coefficient: 
        Applications on Autonomous Robotics. 
        Autonomous Robot Systems (Robotica), 2013 13th International Conference on, 2013.
        
        \bibitem{Geiger} A. Geiger et al,
        Vision meets Robotics: The KITTI Dataset. International Journal of Robotics Research (IJRR), 2013, 
        doi:10.1177/0278364913491297 .
        
        \bibitem{Eugene} Y. K. Eugene and R.G. Johnston, The Ineffectiveness of the Correlation Coefficient for Image Comparisons.
        Technical Report LA-UR-96-2474, Los Alamos, 1996.
        
        %\bibitem{Auoude} G.S. Auoude et al. Sampling-Based Threat Assessment Algorithms for Intersection Collisions Involving 
        %Errant Drivers. IFAC Symposium on Intelligent Autonomous Vehicles, 2010.
        
        %\bibitem{Jonas} T. Jonas, Real-Time Probabilistic Collision Avoidance for Autonomous Vehicles, Using Order Reductive 
        %Conflict Metrics. Submitted to the Department of Aeronautics and Astronautics
	%in partial fulfillment of the requirements for the degree of Doctor of Philosophy. Massachusetts Institute of Technology. June, 2003.
	
	%\bibitem{Woerner} K. Woerner, COLREGS-Compliant Autonomous Collision Avoidance Using Multi-Objective Optimization
	%with Interval Programming. Submitted to the Department of Mechanical Engineering in partial fulfillment of the requirements for the 
	%degrees of Naval Engineer and Master of Science in Mechanical Engineering. Massachusetts Institute of Technology. June, 2014.

\end{thebibliography}

\end{document}
